Behavior Driven Development in Haskell

### 2012-05-23 paper.tex
writing property annotation.

The {\tt container} packages has equation properties:

@@

It is written in code blocks ({\tt >}).
This cannot be used as test case.

>>>>

Haddock also provides code block annotations indicated wwith ({\tt >}).
For example, the {\tt container} packages has the following code block annotation:

@@

\noindent Some Haskellers like this kind of equations and dislike to write it with the example annotation as follow:

\begin{quote}
\begin{verbatim}
> Data.Map.null (empty)
True
\end{verbatim}
\end{quote}

We can see the equation as a boolean property for {\tt null} and {\tt empty} and
can say that there are potentially demands to show properties with Haddock annotation.
But there is no annotation syntax to describe properties in Haddock.
Even if property annotation syntax is defined, 
we have no agreement on how to describe non-boolean properties: e.g. how to specify types of funcation parameters.
